### 2021-04-15 paper.Rmd
typo

\begin{figure*}
   \centering
         \includegraphics[width=\textwidth]{figures/notation-huber.pdf}
\caption{Huber's plot (left) of the penguins data (bill length and depth only). The solid ellipse represents how well the projection, onto different directions, separates the three species and the dashed circle is a reference guide. The histogram (right) is the 1D projection of the data onto the direction outlined as the solid line in the huber's plot. (Adapted from Lee et al. 2005, Figure 1.) }
\label{fig:notation-huber}
\end{figure*}

@@

The authors gratefully acknowledge the support of the Australian Research Council. The paper was written in `rmarkdown` [@Xie2018-bg] using `knitr` [@Xie2017-uh].

>>>>

\begin{figure*}
   \centering
         \includegraphics[width=\textwidth]{figures/notation-huber1.pdf}
         \includegraphics[width=\textwidth]{figures/notation-huber2.pdf}
\caption{Huber's plot (left plots) of the penguins data (bill length and depth only). The solid ellipse represents how well the projection, onto different directions, separates the three species and the dashed circle is a reference guide. The histogram (right) is the 1D projection of the data onto the direction outlined as the solid line in the Huber's plot. (Adapted from Lee et al. 2005, Figure 1.) }
\label{fig:notation-huber}
\end{figure*}

@@

The authors gratefully acknowledge the support of the Australian Research Council. The paper was written in `rmarkdown` [@Xie2018-bg] using `knitr` [@Xie2017-uh]. The source material for this paper is available at \url{https://github.com/dicook/wiley-isghdd}.
